\textbf{The Revised Interoceptive Accuracy Scale (IAS-R) Confirms Links between Interoception and Personality and Psychopathological Traits}

### 2023-03-25 paper/1_Initial/manuscript.Rmd
links

Interoception - definition - is the trending topic. 
Unfortunately, it is also notably hard to measure.

Scales are useful to capture metacognitive and subjective aspects and beliefs
While the relationship between scales and tasks is a strong point of contention, it is important to continue developing sound scales from a structural (i.e., factorial) standpoint.

One of the most recent scale is the IAS, which is interesting because... It has *n* items, such as ...
However, the study analysis did not go in depth in the analysis of the factor structure, focusing instead on ....

The purpose of this work is to re-analyze the factor structure of the scale using complementary statistical approaches. and propose a revised version. And to compare it with one of the most popular questionnaire of interoception, the MAIA-2 (*ref*).

@@

@@

**Scoring**. Each scale can be answered on an analog scale (Disagree - Agree). Items can be averaged per dimension, and dimensions can be averaged to get a general Interoception score.

>>>>

Interoception - definition - is a trending topic, becoming a central mechanism of embodied cognition, and showing a key contribution to higher order processes such as .... 
Unfortunately, it is also notably hard to measure.

Scales are useful to capture metacognitive and subjective aspects and beliefs
While the relationship between interoceptive scales and tasks is a strong point of contention, it is important to continue developing sound scales from a structural (i.e., factorial) standpoint.

One of the most recent scale developped is the IAS, which is interesting because... It has *n* items, such as ...
However, the study analysis did not go in depth in the analysis of the factor structure, focusing instead on ....

The purpose of this work is to re-analyze the factor structure of the scale using complementary statistical approaches, a further extend its validation by comparing a revised version with one of the most popular questionnaire of interoception, the MAIA-2 (*ref*), as well as other relevant indices (such as psychopathological traits).

@@

One of the most intriguing new results was the reilationship between interoceptive abilities and several specific primal world beliefs.

@@

**Scoring**. Each scale can be answered on an analogue scale (Disagree - Agree). Items can be averaged per dimension, and dimensions can be averaged to get a general Interoception score.
